Hospitalizations for psychiatric conditions among adolescents during the COVID-19 pandemic: adapted to CHOP input format

### 2022-02-08 psy_peds_3_CHOP.Rmd
the table 1 was added to CHOP pipeline

```{r}
##percentage
patients_hospitalized_agg_sex_perc <- psyCounts %>%
  left_join( patients_hospitalized_agg_sex, by = c("time_p")) %>% 
  replace_na(list(count_sex = 0))
patients_hospitalized_agg_sex_perc$percentage <- 100*patients_hospitalized_agg_sex_perc$count_sex/patients_hospitalized_agg_sex_perc$count_psy_patients
patients_hospitalized_agg_sex_perc <- patients_hospitalized_agg_sex_perc %>% 
  select( time_p, count= count_psy_patients, sex, count_sex, percentage )
patients_hospitalized_agg_sex_perc %>%
  ggplot(aes(x = time_p, y = percentage, fill = sex)) +
  geom_bar(stat="identity", position = "dodge")+
  scale_fill_manual(values = cbPalette) +
  labs(y = "Percentage ",
       x = time_period,
       title = paste0("Patient (%) per ", time_period," aggregated by sex"),
       subtitle = "Per Sex") + 
  theme(legend.position = "bottom") + 
  geom_smooth(method = "lm", formula = y ~ splines::ns(x, 2), se = TRUE, aes(colour=sex), colour= "black", size = 0.5)
```

# Save the output in a RData file. 
```{r}
site = "CHOP"
patient_count_psy_period_psy$siteid = site 
patient_count_psy_period_psy_clear$siteid = site 
bootstrapped_coefficients_df$siteid = site 
bootstrapped_fitted_df$siteid = site 
ratios_patients_with_without_psy$siteid = site 
quantile_bootstrapped_fitted$siteid = site
perc_disorder_group$siteid = site 
patients_hospitalized_agg_sex_perc$siteid = site 
mental_codes_qc_output$siteid = site

save( count_icd, 
      ratios_patients_with_without_psy,
      patient_count_psy_period_psy,
      patient_count_psy_period_psy_clear,
      bootstrapped_coefficients_df,
      bootstrapped_fitted_df,
      quantile_bootstrapped_fitted,
      perc_disorder_group,
      patients_hospitalized_agg_sex_perc,
      mental_codes_qc_output,
      file = paste0("../output/CHOP/peds_psy_aggResults_", site, ".RData"))

>>>>

```{r}
##percentage
patients_hospitalized_agg_sex_perc <- psyCounts %>%
  left_join( patients_hospitalized_agg_sex, by = c("time_p")) %>% 
  replace_na(list(count_sex = 0))
patients_hospitalized_agg_sex_perc$percentage <- 100*patients_hospitalized_agg_sex_perc$count_sex/patients_hospitalized_agg_sex_perc$count_psy_patients
patients_hospitalized_agg_sex_perc <- patients_hospitalized_agg_sex_perc %>% 
  select( time_p, count= count_psy_patients, sex, count_sex, percentage )
patients_hospitalized_agg_sex_perc %>%
  ggplot(aes(x = time_p, y = percentage, fill = sex)) +
  geom_bar(stat="identity", position = "dodge")+
  scale_fill_manual(values = cbPalette) +
  labs(y = "Percentage ",
       x = time_period,
       title = paste0("Patient (%) per ", time_period," aggregated by sex"),
       subtitle = "Per Sex") + 
  theme(legend.position = "bottom") + 
  geom_smooth(method = "lm", formula = y ~ splines::ns(x, 2), se = TRUE, aes(colour=sex), colour= "black", size = 0.5)
```
## Table 1

```{r}
table1 <- read.csv(file = "../output/CHOP/Table 1.csv")
table1 %>% 
   kable( booktabs = T) %>%
  kableExtra::kable_styling(latex_options = "striped") 
```

# Save the output in a RData file. 
```{r}
site = "CHOP"
patient_count_psy_period_psy$siteid = site 
patient_count_psy_period_psy_clear$siteid = site 
bootstrapped_coefficients_df$siteid = site 
bootstrapped_fitted_df$siteid = site 
ratios_patients_with_without_psy$siteid = site 
quantile_bootstrapped_fitted$siteid = site
perc_disorder_group$siteid = site 
patients_hospitalized_agg_sex_perc$siteid = site 
mental_codes_qc_output$siteid = site
table1$siteid = site

save( count_icd, 
      ratios_patients_with_without_psy,
      patient_count_psy_period_psy,
      patient_count_psy_period_psy_clear,
      bootstrapped_coefficients_df,
      bootstrapped_fitted_df,
      quantile_bootstrapped_fitted,
      perc_disorder_group,
      patients_hospitalized_agg_sex_perc,
      mental_codes_qc_output,
      table1,
      file = paste0("../output/CHOP/peds_psy_aggResults_", site, ".RData"))
